SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-10-05 scipy-1.0/paper.tex
Add scikit links
Draft CiSE 2007 and NumFOCUS paragraphs

In April 2006, Paul
Dubois\footnote{https://mail.python.org/pipermail/numpy-discussion/2006-April/007487.html} wrote
to the NumPy mailing list:
\begin{quote}
IEEE's magazine, Computing in Science and Engineering (CiSE), has asked me
to put together a theme issue on the use of Python in Science and
Engineering. I will write an overview to be accompanied by 3-5 articles [. . .]
that show a diverse set of applications or
tools, to give our readers a sense of whether or not Python might be useful
in their own work.
\end{quote}
In the resulting CiSE May/June 2007 special issue, Paul's overview\cite{dubois2007guest}
stated:
\begin{quote}
LLNL now has many Python-based efforts built from scratch or wrapped around
legacy codes [. . .] hundreds of thousands
of lines of C++, Python, and Fortran 95, all working together just as we hoped,
doing compute-intensive calculations on massively parallel computers.
\end{quote}
%https://www.computer.org/csdl/mags/cs/2007/03/c3007.html
(steering code)
SciPy \cite{oliphant2007python}
IPython \cite{perez2007ipython}
Matplotlib \cite{hunter2007matplotlib}
research applications ...

systems biology\cite{myers2007python},
astronomy\cite{greenfield2007reaching},
robotics\cite{krauss2007python},
nanophotonics\cite{bienstman2007python},
partial differential equations\cite{mardal2007using},
neuroimaging\cite{millman2007analysis},
geographic information systems\cite{shi2007python}, and
education\cite{backer2007computational, myers2007pythona},

@@

In 2012, Perry Greenfield, John Hunter, Jarrod Millman, Travis Oliphant,
and Fernando Perez founded NumFOCUS\footnote{https://numfocus.org}.

over 25 sponsored projects

PyData

everywhere...

@@

@@

We use the following criteria to determine whether or not to include new
functionality in SciPy:
\begin{itemize}
    \item The algorithm is of relevance to multiple fields of science.
    \item The algorithm is demonstrably important.  E.g., it is classic
    enough to be included in textbooks, or it is based on a peer-reviewed article
    which has a significant number of citations.
\end{itemize}

>>>>

In April 2006, Paul
Dubois\footnote{https://mail.python.org/pipermail/numpy-discussion/2006-April/007487.html} wrote
to the NumPy mailing list:
\begin{quote}
IEEE's magazine, Computing in Science and Engineering (CiSE), has asked me
to put together a theme issue on the use of Python in Science and
Engineering. I will write an overview to be accompanied by 3-5 articles [. . .]
that show a diverse set of applications or
tools, to give our readers a sense of whether or not Python might be useful
in their own work.
\end{quote}
In the resulting CiSE May/June 2007 special issue, Paul's overview\cite{dubois2007guest}
stated:
\begin{quote}
LLNL now has many Python-based efforts built from scratch or wrapped around
legacy codes [. . .] hundreds of thousands
of lines of C++, Python, and Fortran 95, all working together just as we hoped,
doing compute-intensive calculations on massively parallel computers.
\end{quote}
While it is now more commonly accepted, Paul took the time to explain to
the 2007 reader that ``interpreted doesn't mean slow or only interactive.''
He also shares his own interest in Python for ``computational steering''
where ``Python serves as the input language to a scientific application, and the actual
computations are performed both in Python itself and in compiled extensions.''
%https://www.computer.org/csdl/mags/cs/2007/03/c3007.html
Using Python for computational steering was one of the earliest uses of Python
in large scientific processing pipelines.
In addition to Paul's overview there were also articles introducing
Python and SciPy \cite{oliphant2007python}, IPython \cite{perez2007ipython},
and  Matplotlib \cite{hunter2007matplotlib}.
In addition to these longer introductory articles, there was a diverse set of
research applications including
systems biology\cite{myers2007python},
astronomy\cite{greenfield2007reaching},
robotics\cite{krauss2007python},
nanophotonics\cite{bienstman2007python},
partial differential equations\cite{mardal2007using},
neuroimaging\cite{millman2007analysis},
geographic information systems\cite{shi2007python}, and
education\cite{backer2007computational, myers2007pythona}.

@@

@@

In 2012, Perry Greenfield, John Hunter, Jarrod Millman, Travis Oliphant,
and Fernando Pérez founded NumFOCUS\footnote{https://numfocus.org}.
NumFOCUS is a 501(c)3 public charity whose mission is to
``promote sustainable high-level programming languages, open code development,
and reproducible scientific research.''
While NumFOCUS is language agnostic, many of the early sponsored projects
came from the scientific Python stack.
Today it has over 25 sponsored projects including NumPy, SciPy, IPython, and
Matplotlib.
Among its other projects, NumFOCUS organizes a global network of 
community driven educational program called PyData.

@@

We use the following criteria to determine whether or not to include new
functionality in SciPy:
\begin{itemize}
    \item The algorithm is of relevance to multiple fields of science.
    \item The algorithm is demonstrably important.  For example, it is classic
    enough to be included in textbooks, or it is based on a peer-reviewed article
    which has a significant number of citations.
\end{itemize}
